Ultrafast manipulation of Heisenberg exchange and Dzyaloshinskii Moriya interactions in antiferromagnetic insulators

### 2019-05-02 Presentation/presentation.tex
asdf
wrap on
paper update

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{../Figures/fm_device.png}
\end{figure}

@@

\begin{frame}
\frametitle{Antiferromagnetic Spintronics}
\begin{figure}
\includegraphics[width=0.8\linewidth]{../Figures/afm_device.png}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Manipulation of the spin state}
\begin{block}{Heisenberg model}
\begin{equation} 
\hat{H} = \sum_{\langle i,j \rangle} J \boldsymbol{S}_i \boldsymbol{S}_j \nonumber
\end{equation}
In antiferromagnets $J > 0$. Mentink, J. H. et al. showed that it is possible to manipulate the exchange constant by applying a laser field. $J = J_0 + \Delta J$.
\end{block}
\end{frame}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{../Figures/dmi_canting.png}
\end{figure}
\end{block}
\end{frame}

\begin{frame}
\frametitle{Manipulation of the spin state}
If we can manipulate $J$ and $D$ we can control the canting angle.
\begin{figure}
\includegraphics[width=1\linewidth]{../Figures/canted_afm.png}
\end{figure}
\end{frame}

@@

>>>>

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage[backend=bibtex,natbib=true,sorting=none,style=nature]{biblatex}
\bibliography{../MT.bib}

@@

%\begin{figure}
%\includegraphics[width=0.5\linewidth]{../Figures/fm_device.png}
%\caption{Source: Wikipedia}
%\end{figure}

\begin{figure}
  \begin{minipage}[c]{0.6\textwidth}
    \includegraphics[width=\textwidth]{../Figures/fm_device.png}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.2\textwidth}
    \caption{Source: Wikipedia} \label{fig:1}
  \end{minipage}
\end{figure}

@@

\begin{frame}
\frametitle{Antiferromagnetic Spintronics}

\begin{figure}
  \begin{minipage}[c]{0.6\textwidth}
    \includegraphics[width=\textwidth]{../Figures/afm_device.png}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.2\textwidth}
    \caption{Source: Nature, Spin transport and spin torque in antiferromagnetic devices} \label{fig:2}
  \end{minipage}
\end{figure}

@@

\begin{frame}
\frametitle{Manipulation of the spin state}
\begin{block}{Heisenberg model}
\begin{equation} 
\hat{H} = \sum_{\langle i,j \rangle} J \boldsymbol{S}_i \boldsymbol{S}_j \nonumber
\end{equation}
In antiferromagnets $J > 0$ ($J < 0$ for ferromagnets). Mentink, J. H. et al. showed that it is possible to manipulate the exchange constant by applying a laser field. $J = J_0 + \Delta J$.
\end{block}
\end{frame}

@@

\begin{figure}
  \begin{minipage}[c]{0.6\textwidth}
    \includegraphics[width=\textwidth]{../Figures/dmi_canting.png}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.2\textwidth}
    \caption{Source: Nanoscale} \label{fig:3}
  \end{minipage}
\end{figure}

\begin{frame}
\frametitle{Manipulation of the spin state}
If we can manipulate $J$ and $D$ we can control the canting angle.
\begin{figure}
\includegraphics[width=1\linewidth]{../Figures/canted_afm.png}
\caption{Source: Kimmel presentation}
\end{figure}
\end{frame}

@@

\begin{frame}
\begin{figure}
  \begin{minipage}[c]{0.5\textwidth}
    \includegraphics[width=\textwidth]{../Figures/NNvsNNN1.pdf}
  \end{minipage}\hfill
  \begin{minipage}[c]{0.5\textwidth}
    \caption{$\frac{J_{1}}{J_{1}^0}$ and $\frac{D_{2,ij}}{D_{2,ij}^0}$ are plotted as function of $\mathcal{E}$. Similar results are obtained in \cite{Mentink2015} for $J_{1}$. Solid lines are for $\omega = 4$ and dashed lines are for $\omega = 14$.}
  \end{minipage}
\end{figure}
\footfullcite{Mentink2015}
\end{frame}
